Measurement of total hadronic differential cross sections in the LArIAT experiment

### 2018-04-19 Chapter-2/2-LArTPCs.tex
s

To the bare bones, a LArTPC is a bulk of liquid argon sandwiched in a flat capacitor, equipped with a light collection system. A uniform electric field of the order of ~500 V/cm is maintained constant between the faces of the capacitor.
Two processes occurs when an ionizing radiation traverses the argon active volume: the argon ionize and scintillates along the charge particle's trajectory. Details on the production and detection of ionization charge and scintillation light are provided in \ref{sec:light} and \ref{sec:light} respectively. The optical part of the detector collects the argon scintillation light in matters of nanoseconds. This flash of light flags the starting time of an event in the chamber, $t_0$. The uniform electric field drifts the electrons from ionization towards the anode plane and the ionized argon towards the cathode.

>>>>

To the bare bones, a LArTPC is a bulk of liquid argon sandwiched in a flat capacitor, equipped with a light collection system. A uniform electric field of the order of 500 V/cm is maintained constant between the faces of the capacitor. The anode is sensitive to ionization charge and it is usually made of two or more planes segmented into multiple parallel sense wires; different geometries for the anode segmentation are under study \cite{1748-0221-8-07-P07002}. Two processes occurs when an ionizing radiation traverses the argon active volume: the argon ionize and scintillates along the charge particle's trajectory. Details on the production and detection of ionization charge and scintillation light are provided in \ref{sec:light} and \ref{sec:light} respectively. The optical part of the detector collects the argon scintillation light in matters of nanoseconds. This flash of light determines the start time of an event in the chamber, $t_0$. The uniform electric field drifts the electrons from ionization towards the anode plane where the anode sense wires see either an induced current by the drifting charge (on induction planes) or the injection of the ionization charge (collection plane) [94] \footnote{The ionized argon also drifts,  in the opposite directions compared to the electrons and with a much longer drift time, given that the drift time is proportional to the particle mass.  Ionized argon is collected on the cathode which is not instrumented, so it is not used to infer information about the interactions in the chamber.}. The arrival time of the charge on the anode sense wires is used to measure the position of the original ionizing radiation in the drift direction. In fact, since the constant electric field implies that the drift velocity is also constant in the chamber, the position of the original ionization is simply given by the multiplication of the drift velocity by the drift time, where we define as ``drift time" the difference between $t_0$ and the charge arrival time on the wire planes. 
Combining the spatial information on the different wire planes results in the mapping of a bi-dimensional projection of the interaction pattern in the plane perpendicular to the drift direction.

Calorimetry
